Prepare Data

### 2021-05-06 src/data-processing/prep_data.Rmd
update data prep when data was available

```{r "get data from Qualtrics", results="hide"}
source(here("src/data-processing/tidy_data.R"))
```

## Check Missing Values

We employ the following criteria:

- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.

```{r "check missings"}

@@

### Dependent Variable
```{r "Dependent Variable", echo=F}
load(here("data/intermediate/cleaned_data.RData"))
d %>%
  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
               values_to = "name",
               names_to = "issue") %>%
  drop_na(name) %>%
  mutate(issue = recode(issue, 
                        `name-C` = "COVID-19",
                        `name-D` = "Defense",
                        `name-E` = "Education",
                        `name-I` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
               values_to = "PT1",
               names_to = "issue1") %>%
  drop_na(PT1) %>%
  mutate(issue1 = recode(issue1, 
                        `PT-C1` = "COVID-19",
                        `PT-D1` = "Defense",
                        `PT-E1` = "Education",
                        `PT-I1` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
               values_to = "PT2",
               names_to = "issue2") %>%
  mutate(issue2 = recode(issue2, 
                        `PT-C2` = "COVID-19",
                        `PT-D2` = "Defense",
                        `PT-E2` = "Education",
                        `PT-I2` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
               values_to = "PT3",
               names_to = "issue3") %>%
  mutate(issue3 = recode(issue3, 
                         `PT-C3` = "COVID-19",
                         `PT-D3` = "Defense",
                         `PT-E3` = "Education",
                         `PT-I3` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
               values_to = "PT4",
               names_to = "issue4") %>%
  mutate(issue4 = recode(issue4, 
                         `PT-C4` = "COVID-19",
                         `PT-D4` = "Defense",
                         `PT-E4` = "Education",
                         `PT-I4` = "Immigration"),
        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
  filter(check == 1) %>%
  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                       `PT1` = "DV: Trait Evaluation",
                       `PT2` = "DV: Favorability",
                       `PT3` = "DV: Representation",
                       `PT4` = "DV: Career Prospects")) %>%
  group_by(issue, dvs) %>%
  summarise(means = mean(value, na.rm=T),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev)) %>%
  ggplot(aes(x = dvs, y = means, colour = issue,
             ymin = lower, ymax = upper, label = issue)) +
  geom_point(position = position_dodge(.2)) + 
  geom_errorbar(position = position_dodge(.2), width = 0) +
  geom_label_repel(nudge_x = 0.35,nudge_y = 0.5, size = 4) + 
  labs(y = "0 (negative) - 10 (positive)", 
       x = "", title = "Evaluation of Politicians") +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  theme_minimal() +
  scale_color_manual(values = fig_cols) +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank()) 
```

@@

  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),

@@

  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),

@@

                        `name-C` = "COVID-19",
                        `name-D` = "Defense",
                        `name-E` = "Education",
                        `name-I` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),

@@

                        `PT-C1` = "COVID-19",
                        `PT-D1` = "Defense",
                        `PT-E1` = "Education",
                        `PT-I1` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),

@@

                        `PT-C2` = "COVID-19",
                        `PT-D2` = "Defense",
                        `PT-E2` = "Education",
                        `PT-I2` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),

@@

                         `PT-C3` = "COVID-19",
                         `PT-D3` = "Defense",
                         `PT-E3` = "Education",
                         `PT-I3` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),

@@

                         `PT-C4` = "COVID-19",
                         `PT-D4` = "Defense",
                         `PT-E4` = "Education",
                         `PT-I4` = "Immigration"),

@@

         compromise = if_else(compromis == "geen compromis", "Compromise", "No Compromise"))%>%

@@

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
               values_to = "name",
               names_to = "issue") %>%
  drop_na(name) %>%
  mutate(issue = recode(issue, 
                        `name-C` = "COVID-19",
                        `name-D` = "Defense",
                        `name-E` = "Education",
                        `name-I` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
               values_to = "PT1",
               names_to = "issue1") %>%
  drop_na(PT1) %>%
  mutate(issue1 = recode(issue1, 
                        `PT-C1` = "COVID-19",
                        `PT-D1` = "Defense",
                        `PT-E1` = "Education",
                        `PT-I1` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
               values_to = "PT2",
               names_to = "issue2") %>%
  mutate(issue2 = recode(issue2, 
                        `PT-C2` = "COVID-19",
                        `PT-D2` = "Defense",
                        `PT-E2` = "Education",
                        `PT-I2` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
               values_to = "PT3",
               names_to = "issue3") %>%
  mutate(issue3 = recode(issue3, 
                         `PT-C3` = "COVID-19",
                         `PT-D3` = "Defense",
                         `PT-E3` = "Education",
                         `PT-I3` = "Immigration")) %>%
  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
               values_to = "PT4",
               names_to = "issue4") %>%
  mutate(issue4 = recode(issue4, 
                         `PT-C4` = "COVID-19",
                         `PT-D4` = "Defense",
                         `PT-E4` = "Education",
                         `PT-I4` = "Immigration"),
        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
  filter(check == 1) %>%
  select(`Gender` = F1,
         `Age` = F2,
         `Education` = F9,
         `Region`  = F3,
         `Urbanness`  = F4,
         `Migration Background`  = F5,
         `Job`  = F7,
         `Income`  = F8,
         `Position: Immigration (%)`  = PreT1,
         `Position: Immigration`  = PreT2,
         `Position: Defense`  = PreT3,
         `Position: Education`  = PreT4,
         `Position: Attitude Women in Politics`  = PreT5,
         `Ideology`  = PreT6,
         `Political Efficacy` = PreT7, 
         `Position: COVID-19 Policy` = PreT8,
         `DV: Trait Evaluation` = PT1,
         `DV: Favorability` = PT2,
         `DV: Representation` = PT3,
         `DV: Career Prospects` = PT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```

>>>>

```{r "get data from Qualtrics", results="hide"}
source(here("src/data-processing/tidy_data.R"))
source(here("src/data-processing/Urbaness.R"))
```

@@

### Dependent Variable
```{r "Dependent Variable", echo=F}
d %>%
  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
               values_to = "name",
               names_to = "issue") %>%
  drop_na(name) %>%
  mutate(issue = recode(issue, 
                        name_C = "COVID_19",
                        name_D = "Defense",
                        name_E = "Education",
                        name_I = "Immigration")) %>%
  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),
               values_to = "PT1",
               names_to = "issue1") %>%
  drop_na(PT1) %>%
  mutate(issue1 = recode(issue1, 
                        PT_C1 = "COVID_19",
                        PT_D1 = "Defense",
                        PT_E1 = "Education",
                        PT_I1 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D2, PT_E2, PT_C2, PT_I2),
               values_to = "PT2",
               names_to = "issue2") %>%
  mutate(issue2 = recode(issue2, 
                        PT_C2 = "COVID_19",
                        PT_D2 = "Defense",
                        PT_E2 = "Education",
                        PT_I2 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D3, PT_E3, PT_C3, PT_I3),
               values_to = "PT3",
               names_to = "issue3") %>%
  mutate(issue3 = recode(issue3, 
                         PT_C3 = "COVID_19",
                         PT_D3 = "Defense",
                         PT_E3 = "Education",
                         PT_I3 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D4, PT_E4, PT_C4, PT_I4),
               values_to = "PT4",
               names_to = "issue4") %>%
  mutate(issue4 = recode(issue4, 
                         PT_C4 = "COVID_19",
                         PT_D4 = "Defense",
                         PT_E4 = "Education",
                         PT_I4 = "Immigration"),
        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
  filter(check == 1) %>%
  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                       PT1 = "DV: Trait Evaluation",
                       PT2 = "DV: Favorability",
                       PT3 = "DV: Representation",
                       PT4 = "DV: Career Prospects")) %>%
  group_by(issue, dvs) %>%
  summarise(means = mean(value, na.rm=T),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev)) %>%
  ggplot(aes(x = dvs, y = means, colour = issue,
             ymin = lower, ymax = upper, label = issue)) +
  geom_point(position = position_dodge(.2)) + 
  geom_errorbar(position = position_dodge(.2), width = 0) +
  geom_label_repel(nudge_x = 0.35,nudge_y = 0.5, size = 4) + 
  labs(y = "0 (negative) - 10 (positive)", 
       x = "", title = "Evaluation of Politicians") +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  theme_minimal() +
  scale_color_manual(values = fig_cols) +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank()) 
```

@@

  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),

@@

  pivot_longer(cols = c(name_D, name_I, name_E, name_C),

@@

                        name_C = "COVID_19",
                        name_D = "Defense",
                        name_E = "Education",
                        name_I = "Immigration")) %>%
  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),

@@

                        PT_C1 = "COVID_19",
                        PT_D1 = "Defense",
                        PT_E1 = "Education",
                        PT_I1 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D2, PT_E2, PT_C2, PT_I2),

@@

                        PT_C2 = "COVID_19",
                        PT_D2 = "Defense",
                        PT_E2 = "Education",
                        PT_I2 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D3, PT_E3, PT_C3, PT_I3),

@@

                         PT_C3 = "COVID_19",
                         PT_D3 = "Defense",
                         PT_E3 = "Education",
                         PT_I3 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D4, PT_E4, PT_C4, PT_I4),

@@

                         PT_C4 = "COVID_19",
                         PT_D4 = "Defense",
                         PT_E4 = "Education",
                         PT_I4 = "Immigration"),

@@

         compromise = if_else(compromis == "geen compromis", "Compromise", "No Compromise")) %>%

@@

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
               values_to = "name",
               names_to = "issue") %>%
  drop_na(name) %>%
  mutate(issue = recode(issue, 
                        `name_C` = "COVID_19",
                        `name_D` = "Defense",
                        `name_E` = "Education",
                        `name_I` = "Immigration")) %>%
  pivot_longer(cols = c(`PT_D1`, `PT_E1`, `PT_C1`, `PT_I1`),
               values_to = "PT1",
               names_to = "issue1") %>%
  drop_na(PT1) %>%
  mutate(issue1 = recode(issue1, 
                        `PT_C1` = "COVID_19",
                        `PT_D1` = "Defense",
                        `PT_E1` = "Education",
                        `PT_I1` = "Immigration")) %>%
  pivot_longer(cols = c(`PT_D2`, `PT_E2`, `PT_C2`, `PT_I2`),
               values_to = "PT2",
               names_to = "issue2") %>%
  mutate(issue2 = recode(issue2, 
                        `PT_C2` = "COVID_19",
                        `PT_D2` = "Defense",
                        `PT_E2` = "Education",
                        `PT_I2` = "Immigration")) %>%
  pivot_longer(cols = c(`PT_D3`, `PT_E3`, `PT_C3`, `PT_I3`),
               values_to = "PT3",
               names_to = "issue3") %>%
  mutate(issue3 = recode(issue3, 
                         `PT_C3` = "COVID_19",
                         `PT_D3` = "Defense",
                         `PT_E3` = "Education",
                         `PT_I3` = "Immigration")) %>%
  pivot_longer(cols = c(`PT_D4`, `PT_E4`, `PT_C4`, `PT_I4`),
               values_to = "PT4",
               names_to = "issue4") %>%
  mutate(issue4 = recode(issue4, 
                         `PT_C4` = "COVID_19",
                         `PT_D4` = "Defense",
                         `PT_E4` = "Education",
                         `PT_I4` = "Immigration"),
        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
  filter(check == 1) %>%
  select(`Gender` = F1,
         `Age` = F2,
         `Education` = F9,
         `Region`  = F3,
         `Urbanness`  = F4,
         `Migration Background`  = F5,
         `Job`  = F7,
         `Income`  = F8,
         `Position: Immigration (%)`  = PreT1,
         `Position: Immigration`  = PreT2,
         `Position: Defense`  = PreT3,
         `Position: Education`  = PreT4,
         `Position: Attitude Women in Politics`  = PreT5,
         `Ideology`  = PreT6,
         `Political Efficacy` = PreT7, 
         `Position: COVID-19 Policy` = PreT8,
         `DV: Trait Evaluation` = PT1,
         `DV: Favorability` = PT2,
         `DV: Representation` = PT3,
         `DV: Career Prospects` = PT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```
